Self Regulation Ontology Retest Data Report

### 2017-03-21 SRO_Report.Rmd
working on new report

### Relationship between ICC and Spearman

```{r}
icc_df %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  ggplot(aes(spearman, icc, col=task))+
  geom_point()+
  theme_bw()
```

>>>>

Sort tasks by icc. What's going on with the negative icc's?
ICC(3,k) would be negative if the $MS_{error}$>$MS_{between}$

Plot their data scatter plots.
```{r, fig.height=12, fig.width=12}
neg_icc_vars = icc_df %>%
  arrange(icc) %>% 
  filter(icc<0) %>%
  select(dv)

tmp = data.frame()

for(i in 1:nrow(neg_icc_vars)){
  tmp = rbind(tmp, match_t1_t2(neg_icc_vars$dv[i]))
}
rm(neg_icc_vars)

tmp %>%
  spread(time, score) %>%
  ggplot(aes(`1`, `2`))+
  geom_point()+
  theme_bw()+
  facet_wrap(~dv, scales='free')

```

Compare these plots to the variables with highest icc

```{r fig.height=12, fig.width=12}
high_icc_vars = icc_df %>%
  arrange(-icc)  %>% 
  filter(icc>0.92) %>%
  select(dv)

tmp = data.frame()

for(i in 1:nrow(high_icc_vars)){
  tmp = rbind(tmp, match_t1_t2(high_icc_vars$dv[i]))
}
rm(high_icc_vars)

tmp %>%
  spread(time, score) %>%
  ggplot(aes(`1`, `2`))+
  geom_point()+
  theme_bw()+
  facet_wrap(~dv, scales='free')

```

```{r echo=FALSE}
rm(tmp)
```

### Relationship between ICC and Spearman
Mostly linear except for a bunch of tasks that have an icc ~ 0.

```{r}
icc_df %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  ggplot(aes(spearman, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank())
```

What are the variables clustered around 0 ICC?

```{r}
icc_df %>%
  filter(icc>(-0.1), icc<0.1) %>%
  arrange(icc)
```

### Relationship between ICC and $\eta^2$

```{r}
icc_df %>%
  ggplot(aes(eta_sq, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank())
```

Which tasks show a systematic difference between t1 and t2?
Are these the tasks where the ICC and Spearman imply different conclusions?

```{r}
icc_df %>%
  select(dv, eta_sq) %>%
  arrange(-eta_sq)
```
